---
title: "bay-do-modeled-vs-observed"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bay-do-modeled-vs-observed}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bayTools)
```

In this document, we will explore observed dissolved oxygen concentrations from continuous monitoring stations operated in the Potomac River by Maryland, Virginia, and the U.S. federal government.

We will be specifically investigating observed dissolved oxygen concentrations in contrast with predicted dissolved oxygen equilibrium concentrations from standard physical models based on water temperature, salinity, and atmospheric pressure. 

Before we can begin our analysis, we must compile all necessary data. For now, we can start with a dataset of MD "Eyes on the Bay" continuous monitoring station data.

```{r}
# MD EOTB: https://eyesonthebay.dnr.maryland.gov/

# look at just one station, Mallow's Bay (MAB)
load(file.path(getwd(), '..', 'data', 'conmon_eotb.rda'))

eotb <- conmon_eotb_2001_2022 %>%
  filter(grepl('XDA8236', station))

head(eotb) 

eotb.min <- eotb %>%
  mutate(
    date = lubridate::as_date(date_time),
    year = lubridate::year(date),
  ) %>%
  group_by(station, year, date) %>%
  summarize(
    do_min = min(do),
    do_min_time = format(date_time[which(do == do_min)], format = "%H:%M"),
    year = max(year),
    month = max(lubridate::month(date)),
    quarter = max(lubridate::quarter(date)),
  ) %>%
  filter(
    year == 2019,
  )

gg.mab <- ggplot(eotb.min) +
  geom_point(aes(x = date, y = do_min_time, col = do_min)) +
  facet_wrap(~year)

gg.mab

```
